CRDS Server Documentation

### 2014-07-17 docs/server_guide/build/latex/crds_server.tex
More server_guide.
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@1564 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

e.g. /ifs/crds/jwst/test/file\_cache
\end{quote}

Each CRDS server (test or ops) has a full copy (\textasciitilde{}2T allocation) of all operational and historical (CRDS-only)
reference files. The dev servers have a smaller allocation which is generally linked to /grp/crds
(synced from ops servers) rather than internally stored.

>>>>

e.g. /ifs/crds/jwst/test/file\_cache/\{config,mappings,references\}/\{hst,jwst\}
\end{quote}

Each CRDS server (test or ops) has a full copy (\textasciitilde{}2T allocation) of all operational and historical (CRDS-only)
reference files and rules. The dev servers have a smaller allocation which is generally linked to /grp/crds
(synced from ops servers) rather than internally stored.
